The ChEMBL database as Linked Open Data

### 2012-08-14 article.tex
Added a citation for VOS
Added the Nature Precedings presentation for CitedIn

To expose the ChEMBL-RDF data two approaches have been adopted. First, a SPARQL end point is being
hosted at Uppsala University, using the Open Source Virtuoso software. Usage is free, but the
allowed volume of querying is capped, based on the estimated computational effort. Second, resources have
been made dereferencable via the \url{http://linkedchemistry.info} resource. The Kasabi
platform~\cite{kasabi} was used for a period of time, until that project was discontinued.
The Uppsala SPARQL end point still uses resource URIs based on the Kasabi approach, following a similar
URI pattern where linkedchemistry.info/chembl is replaced by data.kasabi.com/dataset/chembl-rdf.

@@

Using the SPARQL end point, it is easy to integrate data from ChEMBL into other web resources, such as CitedIn (http://www.citedin.org).
While the impact of a scientific publication is traditionally measured by frequency of citation in subsequent publications, this
narrowly defined calculation increasingly fails to capture the true reach of a paper. CitedIn was developed to make scientific
impact more visible and more accurate by providing insight into where published work is being cited online in a variety of public
resources. ChEMBL contains many literature references. The SPARQL endpoint is queried by CitedIn and the results are presented to its users.
Figure~\ref{fig:citedin} shows the results for the Nature paper by Gamo presenting the malaria structures~\cite{Gamo2010}
which is cited as the reference for a large number of activity datapoints and compounds in ChEMBL.
Counting all objects that reference this paper is done by the following SPARQL query:

>>>>

To expose the ChEMBL-RDF data two approaches have been adopted. First, a SPARQL end point is being
hosted at Uppsala University, using the Open-Source Edition of the Virtuoso software~\cite{Virtuoso}. Usage is free, but the
allowed volume of querying is capped, based on the estimated computational effort. Second, resources have
been made dereferencable via the \url{http://linkedchemistry.info} resource. The Kasabi
platform~\cite{kasabi} was used for a period of time, until that project was discontinued.
The Uppsala SPARQL end point still uses resource URIs based on the Kasabi approach, following a similar
URI pattern where linkedchemistry.info/chembl is replaced by data.kasabi.com/dataset/chembl-rdf.

@@

Using the SPARQL end point, it is easy to integrate data from ChEMBL into other web resources, such as CitedIn (http://www.citedin.org)~\cite{CitedIn2011}.
While the impact of a scientific publication is traditionally measured by frequency of citation in subsequent publications, this
narrowly defined calculation increasingly fails to capture the true reach of a paper. CitedIn was developed to make scientific
impact more visible and more accurate by providing insight into where published work is being cited online in a variety of public
resources. ChEMBL contains many literature references. The SPARQL endpoint is queried by CitedIn and the results are presented to its users.
Figure~\ref{fig:citedin} shows the results for the Nature paper by Gamo presenting the malaria structures~\cite{Gamo2010}
which is cited as the reference for a large number of activity datapoints and compounds in ChEMBL.
Counting all objects that reference this paper is done by the following SPARQL query:
